---
title: "Weight of Fish"
author: "Ambar Arreola"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
require(car)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```





### Best Two regressor model

Best two regression models are height and width.

```{r}
Perchmodel <-lm(Weight~Height+Width, data=Perch)
summary.lm(Perchmodel)
```
The adjusted r-square is 0.94 and the residual standard error is 85.17 with a p-value of 2.2.


```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

The base model is the two element model 
## Pike
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

L1,L3 are the two best regressor model.Best regression model is everything.

### Best Models
```{r}
Pikebest <-lm(Weight~.,data=Pike)
summary.lm(Pikebest)
```

The R-squared is 0.9794 and the residual error is 70.86. The p-value is 8.679. This is the best model.
 

### Best Two regressor model


```{r}
Piketwo <-lm(Weight~Length1+Length3, data=Pike)
summary.lm(Piketwo)
```

This model summarizes our bst two regression models. The residual standard error is 92.56 the r squared is and the  p value is 2.572e-11. The smallest p-value has the best result.

## Roach


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

Best regression model is all of them. The tqo  is L1,L2,L3,H-W

### Best Models

```{r}
Roachbest <-lm(Weight~.,data=Roach)
summary.lm(Roachbest)
```
The residual standard error is 37.58. the r-squared is 0.821 and the p-value us 1.028e-05.This model has the smallest p-value of all the models that have been completed so far.



### Best Two regressor model

```{r}
Roachtwo <-lm(Weight~Length1+Length3, data=Roach)
summary.lm(Roachtwo)
```
The residual standard error is 36.83. the r squared is 0.8281 and the Pvalue is 1.23e-07. This model has the second to smallest p-value of all of the above.

## Final Summary Statements